An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-10-13 aistats2017.tex
fixes to text

\begin{abstract}
  %The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
  %both left and right-hand margins. Use 10~point type, with a vertical
  %spacing of 11~points. The {\bf Abstract} heading must be centered,
  %bold, and in point size 12. Two line spaces precede the
  %Abstract. The Abstract must be limited to one paragraph.
  Markov chain Monte Carlo (MCMC) methods have many applications in
  machine learning. We are particularly interested in their application
  to modeling very large datasets, where it is impractical to perform
  Metropolis-Hastings tests on the full data. Previous work on reducing
  the cost of Metropolis-Hastings tests yield variable data consumed per
  sample, with only constant factor reductions versus using the full
  dataset for each sample.  Here we present a method that can be tuned
  to provide arbitrarily small batch sizes, by adjusting either proposal
  step size or temperature. Our approach uses the natural noise present
  in minibatch likelihood estimates to furnish the randomness in a
  Metropolis-Hastings test. Our test uses the noise-tolerant Barker
  acceptance test with a novel additive correction variable.  The
  resulting test can be combined with minibatch proposals to yield
  updates with the same complexity as a simple SGD update. In this paper
  we derive the test, analyze its performance, discuss its
  implementation, and present several experiments. We demonstrate 
  order-of-magnitude speedups over previous work, and show for
  the first time that small expected minibatch sizes are possible. 
\end{abstract}

@@

    \item Increase the minibatch size when needed. Log acceptance variance
    scales as $1/k$ vs the minibatch size $k$. Our test is adaptive like earlier
    works, but unlike them, the distribution of minibatch size is Gaussian, not
    long-tailed.  Increased minibatch size also reduces the error rate for the
    test.

    \item For continuous distributions, reduce the proposal step size and
    variance compared to an optimal proposal. The variance of the log acceptance
    probability scales as the square of proposal step size. 
\end{itemize}

It is worth discussing at this point the typical goals of M-H sampling on large
datasets. By the Bernstein-von Mises Theorem, the posterior distribution for a
Bayesian inference task has variance that scales inversely with $N$. Simply
sampling from it is one application, but an efficient
proposal~\citep{OptimalScaling01} has similar variance to the target and will
diffuse to it extremely slowly. For applications to neural networks or models
where the posterior is multimodal~\citep{choromanska2014loss}, samplers will
likely get trapped in one of the modes. A common solution is to anneal the
sampler, running first at high temperatures to flatten the likelihood landscape.
This in turn reduces the variance of the log acceptance probability and allows
our test to be applied. Our samples can cover the search space densely with
small steps rather than taking a few sparse steps towards an optimum. In this
mode, Metropolis-Hastings can be used in similar fashion to Stochastic Gradient
Descent. The goal in SGD is to make gradual progress to a posterior mode with
each step, taking small steps so that the cumulative displacement has
progressively lower variance.

@@

This result is used in~\citet{Barker65} to define the Barker acceptance test.  As
a sanity check, choosing $g(s) = \exp(s) \wedge 1$ --- a function satisfying the
requirement of Lemma~\ref{lem:detailed_balance} --- produces the classical
Metropolis acceptance test $\alpha(\theta,\theta') = g(\Delta(\theta,\theta')) =
\frac{p(\theta')q(\theta \mid \theta')}{p(\theta)q(\theta' \mid \theta)}\wedge
1$. In fact, $g(s) =\exp(s) \wedge 1$ is the optimal acceptance function in
terms of acceptance rate, since it accepts with probability 1 for $\Delta > 0$.

\subsection{Barker (Logistic) Acceptance Function}\label{ssec:barker_function}
For our new MH test we use the Barker logistic~\citep{Barker65} function:
$g(s)=(1+\exp(-s))^{-1}$. Straightforward arithmetic shows that it satisfies the
condition in Lemma~\ref{lem:detailed_balance}.  While it is slightly less
efficient than the Metropolis test when used on the full dataset, we will see
that its smoothness allows it to naturally tolerate substantial variance in its
input. This in turn will lead to a much more efficient test on subsets of data.

@@

In the limit, since $\Delta^*$ is normally distributed about its mean $\Delta$,
we can write
\begin{equation}\label{eq:relationship}
    \Delta^* = \Delta + X_{\rm norm}, \quad X_{\rm norm} \sim \mathcal{\bar{N}}(0, \sigma^2(\Delta^*)),
\end{equation}
where $\mathcal{\bar{N}}(0, \sigma^2(\Delta^*))$ denotes a distribution which is
approximately normal with variance $\sigma^2(\Delta^*)$.  But to perform the
test in Equation~(\ref{eq:the_exact_test}) we want $\Delta + X$ for a logistic
random variable $X$ (call it $X_{\rm log}$ from now on). In~\citet{TallData15} it
was proposed to use $\Delta^*$ in a Barker test anyway and tolerate the fixed
error caused by this approximation.

@@

To apply this to our test, let $X_i = \Lambda_i(\theta,\theta') -
\Lambda(\theta,\theta')$, so that the $X_i$ are zero-mean, i.i.d. variables. If
instead of all $n$ samples, we only extract a subset of $b$ samples
corresponding to our minibatch, we can connect $\bar{X}$ with our $\Delta^*$
term: $\bar{X} = \Delta^*(\theta,\theta') - \Delta(\theta,\theta')$, so that
$s_X = s_{\Delta^*}$. This results in the following:

\begin{corollary}\label{cor:our_bound_delta_prime}
We can now substitute into Equation~(\ref{eq:clt-bounds2}) and displace by the mean, giving:
\begin{align*}
    \sup_y\left|{\rm Pr}(\Delta^*< y) - \Phi\left(\frac{y-\Delta}{s_{\Delta^*}}\right)\right| &\leq \frac{6.4E|X|^3+2E|X|}{\sqrt{b}} \\
    &= \epsilon(\theta,\theta',b).
\end{align*}
\end{corollary} %\vspace{-10pt}
Corollary~\ref{cor:our_bound_delta_prime} shows that the distribution of
$\Delta^*$ approximates a Normal distribution with mean $\Delta$ and variance
$s^2_{\Delta^*}$. Furthermore, it bounds the error with \emph{estimable
quantities}: both $E|X|$ and $E|X|^3$ can be estimated as means of $|\Lambda_i
- \Lambda|$ and $|\Lambda_i - \Lambda|^3$, respectively, on each minibatch. We
expect this will often be accurate enough on minibatches with hundreds of
points, but otherwise bootstrap CIs can be computed.

@@

We first borrow a Gaussian mixture experiment from~\citet{langevin_2011}.  The
parameter is 2-D, $\theta = \langle \theta_1,\theta_2 \rangle$, and the
generation process is
\begin{equation}\label{eq:data_generation}
\begin{split}
    \theta &\sim \mathcal{N}(0, {\rm diag}(\sigma_1^2,\sigma_2^2)) \\
    x_i & \sim 0.5 \cdot \mathcal{N}(\theta_1, \sigma_x^2) + 0.5 \cdot \mathcal{N}(\theta_1+\theta_2, \sigma_x^2).
\end{split}
\end{equation}
We set $\sigma_1^2 = 10, \sigma_2^2 = 1$ and $\sigma_x^2=2$.  We fix $\theta =
\langle 0,1 \rangle$. The original paper sampled 100 data points and estimated
the posterior. We are interested in performance on larger problems and so
sampled 1,000,000 points to form the posterior of
$p(\theta)\prod_{i=1}^{1,000,000}p(x_i\mid \theta)$ with the same prior from
Equation~(\ref{eq:data_generation}). This produces a much sharper posterior with
two very narrow peaks.  Our goal is to reproduce the original posterior, so we
adjust the temperature to $T=10,000$.  Taking logs, we get the target as shown
in the far left of Figure~\ref{fig:gauss_mix_1}.

We run MCMC with our test and benchmark with~\citet{cutting_mh_2014}
and~\citet{icml2014c1_bardenet14}, all with initial minibatch size 100.  For the
former, we increment sizes by 100 and set the tolerance $\epsilon=0.005$.  For
the latter, we increase sizes geometrically with $\gamma = 1.5$ and use
parameters $p = 2, \delta = 0.01$.  All methods collect 5000 samples using a
random walk proposer with covariance ${\rm diag}(0.15, 0.15)$, which means the
M-H test is responsible for the sample distribution.

@@

We discretize the posterior coordinates into bins with respect to the two
components of $\theta$.  The probability $P_i$ of a sample falling into bin $i$
is the integral of the true posterior over the bin's area.  A single sample
should therefore be multinomial with distribution $P$, and a set of $n$ (ideally
independent) samples is ${\rm Multinomial}(P,n)$. This distribution is simple
and we can use it to measure the quality of the samples rather than use general
purpose tests like KL-divergence or likelihood-ratio, which can be problematic
with zero counts in bins.

For large $n$, the per-bin distributions are approximated by Poissons with
parameter $\lambda_i=P_i n$. Given samples $\{\theta_1,\ldots,\theta_T\}$, let
$c_j$ denote the number of individual samples $\theta_i$ that fall in bin $j$
out of $N_{\rm bins}$ total. We have
\begin{equation}\label{eq:log_prob_poissons}
\begin{split}
    \log p(c_1, \ldots, c_{N_{\rm bins}} \mid P_1, \ldots, P_{N_{\rm bins}}) & =  \\
    \sum_{j=1}^{N_{\rm bins}} c_j \log (n P_j) - n P_j - \log(\Gamma(c_j+1)). & \\
\end{split}
\end{equation}
Table~\ref{tab:poissons} shows the results, but it is difficult to interpret the
scores, so we perform significance tests to show the difference between the
MCMC-samples and ground-truth using the Chi-Squared distribution as the test
statistic (also in Table~\ref{tab:poissons}). Both metrics imply that our method
is slightly superior to~\citet{cutting_mh_2014}, but slightly worse
than~\citet{icml2014c1_bardenet14}.

Figure~\ref{fig:gauss_mix_2}, however, suggests that our method dominates in
terms of speed and efficiency. The histograms of the (final) minibatch sizes
used each iteration show that our method consumes significantly less data; the
distribution is short-tailed and the mean is 210, more than an order of
magnitude better compared to the other two methods (averages are 15562 and
16857). The sizes roughly predict the running times of these methods, which are
proportional to the data consumed, with the exception of the
$C_{\theta,\theta'}$ time for~\citet{icml2014c1_bardenet14}. Using minibatch
sizes as a proxy for time also avoids discrepancies due to code optimization.

@@

We next use logistic regression for the binary classification of 1s versus 7s on
a subset of the MNIST8M dataset, a larger version of
MNIST~\citep{lecun-mnisthandwrittendigit-2010} and well-suited to our big data
objectives. We randomly subsampled 450k training and 192k testing points. The
pixels are scaled in $[0,1]$. We impose a flat prior on $\theta$ and again use a
random walk proposer, this time with covariance matrix $0.05I$ for the
$784\times 784$ identity matrix $I$. The temperature is set at $T=1000$. We run
the three tests for samples and again use 100 as the starting minibatch size. To
make~\citet{cutting_mh_2014} run faster, we now use $\epsilon=0.05$.
For~\citet{icml2014c1_bardenet14}, we tuned $\gamma \in \{1.1,1.25,1.5,1.75,2\}$
before concluding that $\gamma=2.0$ was OK. In addition, we tried their analytic
approximation to $C_{\theta,\theta'}$, but found that the bounds were too high,
meaning that their method needed to consume the entire dataset each iteration.
Thus, we naively compute $C_{\theta,\theta'}$.

@@

We demonstrate how we can show $O(n^{-1})$ error for the quantitative CLT by
using a more precise limit distribution under an additional assumption. Let
$\mu_i$ denote the $i^{th}$ moment, and $b_i$ denote the $i^{th}$ absolute
moment of $X$. If Cramer's condition holds:
\begin{equation}\label{eq:cramers_condition}
    \lim_{t \to \infty} \sup |E(\exp(i t X))| < 1,
\end{equation}
then Equation 2.2 in Bentkus et al.'s work on Edgeworth
expansions~\citep{Bentkus97} provides:

@@

We previously submitted a much older draft of this paper to NIPS 2016. The
current manuscript has been substantially revised since that submission. We have
made the following changes:

\begin{enumerate}
    \item At the time of the NIPS submission, we were unaware of several
    references which described some of what we wrote. For this submission, we
    now cite the important work of~\citep{TallData15} which had the idea of
    using subsampling noise for exploration (rather than the $\log u$ variable).
    We also cite the work of~\citep{Barker65} which uses the Barker function. We
    welcome information about other potentially missing references.

    \item The previous theoretical results have been entirely scrapped and
    replaced with different but more relevant results. The NIPS submission
    listed a page of theoretical results which did not tie into the rest of the
    paper's contributions and were confusing to the readers. We now have
    theoretical results that are much clearer and also \emph{directly} show the
    expected performance benefits of our acceptance test. Note also that
    Lemma~\ref{lem:worst_case} is an entirely new addition to this version.

    \item Several reviewers mentioned that our deconvolution approach to
    determine the correction distribution was not unique and thus ill-defined.
    Consequently, we have added an entirely new section of the paper
    (Section~\ref{sec:correction}) explaining how we derived that distribution.

    \item Reviewers pointed out one of our mistakes when we said our minibatch
    sizes were fixed. We have changed this in the current manuscript to mean
    that the per-iteration minibatch sizes for our test have a distribution with
    \emph{shorter tails} than those of prior work, which can be observed by
    plotting a histogram of minibatch sizes.

    \item Our experiments now include new comparisons with a baseline
    from~\citep{icml2014c1_bardenet14} (in addition to~\citep{cutting_mh_2014},
    which we had earlier). In addition, each algorithm now runs MCMC sampling on
    the \emph{same} distribution.  Previously, we ran our distribution at a
    higher temperature but kept the algorithm from~\citep{cutting_mh_2014}
    running on the distribution at temperature $T=1$. In this set of
    experiments, we tuned hyperparameters of the other algorithms to make the
    comparison fairer. Finally, in the Gaussian mixture model scenario
    (Section~\ref{ssec:gaussians}), we provide more details on how ``accurate''
    the samples are, rather than solely relying on the visualization of
    Figure~\ref{fig:gauss_mix_1}.

@@

We are confident that the current manuscript is of far better quality than the
NIPS submission, and we appreciate the efforts of the NIPS reviewers to give us
ideas for improvement.

>>>>

\begin{abstract}
  %The Abstract paragraph should be indented 0.25 inch (1.5 picas) on
  %both left and right-hand margins. Use 10~point type, with a vertical
  %spacing of 11~points. The {\bf Abstract} heading must be centered,
  %bold, and in point size 12. Two line spaces precede the
  %Abstract. The Abstract must be limited to one paragraph.
  We
  present a novel Metropolis-Hastings method for large datasets that
  uses small expected-size minibatches of data. Previous work on
  reducing the cost of Metropolis-Hastings tests yield variable data
  consumed per sample, with only constant factor reductions versus
  using the full dataset for each sample.  Here we present a method
  that can be tuned to provide arbitrarily small batch sizes, by
  adjusting either proposal step size or temperature. Our test uses
  the noise-tolerant Barker acceptance test with a novel additive
  correction variable.  The resulting test has simlar cost to a normal
  SGD update. Our experiments demonstrate several order-of-magnitude
  speedup over previous work.
\end{abstract}

@@

    \item For continuous distributions, reduce the proposal step size and
    variance compared to an optimal proposal. The variance of the log acceptance
    probability scales as the square of proposal step size.

%  \item Increase the minibatch size when needed. Log acceptance variance
%    scales as $1/k$ vs the minibatch size $k$. Our test is adaptive like earlier
%    works, but unlike them, the distribution of minibatch size is Gaussian, not
%    long-tailed.  Increased minibatch size also reduces the error rate for the
%    test.
\end{itemize}

It is worth discussing at this point the typical goals of M-H sampling on large
datasets. By the Bernstein-von Mises Theorem, the posterior distribution for a
Bayesian inference task has variance that scales inversely with $N$. Simply
sampling from it is one application, but an efficient
proposal~\citep{OptimalScaling01} has similar variance to the target and will
diffuse to it extremely slowly. For applications to neural networks or models
where the posterior is multimodal~\citep{choromanska2014loss}, samplers will
likely get trapped in one of the modes. A common solution is to anneal the
sampler, running first at high temperatures to flatten the likelihood landscape.
This in turn reduces the variance of the log acceptance probability and allows
our test to be applied. Theses samples can cover the search space densely with
small steps rather than taking a few sparse steps towards an optimum. In this
mode, Metropolis-Hastings can be used in similar fashion to Stochastic Gradient
Descent. The goal in SGD is to make gradual progress to a posterior mode with
each step, taking small steps so that the cumulative displacement has
progressively lower variance.

@@

This result is used in~\citet{Barker65} to define the Barker acceptance test.
%As
%a sanity check, choosing $g(s) = \exp(s) \wedge 1$ --- a function satisfying the
%requirement of Lemma~\ref{lem:detailed_balance} --- produces the classical
%Metropolis acceptance test $\alpha(\theta,\theta') = g(\Delta(\theta,\theta')) =
%\frac{p(\theta')q(\theta \mid \theta')}{p(\theta)q(\theta' \mid \theta)}\wedge
%1$.
%In fact, $g(s) =\exp(s) \wedge 1$ is the optimal acceptance function in
%terms of acceptance rate, since it accepts with probability 1 for $\Delta > 0$.

\subsection{Barker (Logistic) Acceptance Function}\label{ssec:barker_function}
For our new MH test we use the Barker logistic~\citep{Barker65}
function: $g(s)=(1+\exp(-s))^{-1}$. Straightforward arithmetic shows
that it satisfies the condition in Lemma~\ref{lem:detailed_balance}.
It is slightly less efficient than the Metropolis test, since its
acceptance rate for vanishing likelihood difference is 0.5. However we
will see that its overall sample efficiency is much higher than the
earlier methods.

@@

In the limit, since $\Delta^*$ is normally distributed about its mean $\Delta$,
we can write
\begin{equation}\label{eq:relationship}
    \Delta^* = \Delta + X_{\rm norm}, \quad X_{\rm norm} \sim \mathcal{\bar{N}}(0, \sigma^2(\Delta^*)),
\end{equation}
where $\mathcal{\bar{N}}(0, \sigma^2(\Delta^*))$ denotes a distribution which is
approximately normal with variance $\sigma^2(\Delta^*)$.  But to perform the
test in Equation~(\ref{eq:the_exact_test}) we want $\Delta + X$ for a logistic
random variable $X$ (call it $X_{\rm log}$ from now on). In~\citet{TallData15} it
was proposed to use $\Delta^*$ in a Barker test, and tolerate the fixed
error between logistic and normal distributions.

@@

To apply this to our test, let $X_i = \Lambda_i(\theta,\theta') -
\Lambda(\theta,\theta')$, so that the $X_i$ are zero-mean, i.i.d. variables. If
instead of all $n$ samples, we only extract a subset of $b$ samples
corresponding to our minibatch, we can connect $\bar{X}$ with our $\Delta^*$
term: $\bar{X} = \Delta^*(\theta,\theta') - \Delta(\theta,\theta')$, so that
$s_X = s_{\Delta^*}$. We can now substitute into Equation~(\ref{eq:clt-bounds2}) and displace by the mean, giving:

\begin{corollary}\label{cor:our_bound_delta_prime}
\begin{align*}
    \sup_y\left|{\rm Pr}(\Delta^*< y) - \Phi\left(\frac{y-\Delta}{s_{\Delta^*}}\right)\right| &\leq \frac{6.4E|X|^3+2E|X|}{\sqrt{b}} \\
    &= \epsilon(\theta,\theta',b).
\end{align*}
\end{corollary} %\vspace{-10pt}
Corollary~\ref{cor:our_bound_delta_prime} shows that the distribution of
$\Delta^*$ approximates a Normal distribution with mean $\Delta$ and variance
$s^2_{\Delta^*}$. Furthermore, it bounds the error with \emph{estimable
quantities}: both $E|X|$ and $E|X|^3$ can be estimated as means of $|\Lambda_i
- \Lambda|$ and $|\Lambda_i - \Lambda|^3$, respectively, on each minibatch. We
expect this will often be accurate enough on minibatches with hundreds of
points, but otherwise bootstrap CIs can be computed.

@@

This model is adapted from~\citet{langevin_2011} by increasing the number
of samples to 1 million.  The parameters are $\theta = \langle \theta_1,\theta_2 \rangle$, and the
generation process is
\begin{equation}\label{eq:data_generation}
\begin{split}
    \theta &\sim \mathcal{N}(0, {\rm diag}(\sigma_1^2,\sigma_2^2)) \\
    x_i & \sim 0.5 \cdot \mathcal{N}(\theta_1, \sigma_x^2) + 0.5 \cdot \mathcal{N}(\theta_1+\theta_2, \sigma_x^2).
\end{split}
\end{equation}
We set $\sigma_1^2 = 10, \sigma_2^2 = 1$ and $\sigma_x^2=2$.  We fix $\theta =
\langle 0,1 \rangle$. The original paper sampled 100 data points and estimated
the posterior. We are interested in performance on larger problems and so
sampled 1,000,000 points to form the posterior of
$p(\theta)\prod_{i=1}^{1,000,000}p(x_i\mid \theta)$ with the same prior from
Equation~(\ref{eq:data_generation}). This produces a much sharper posterior with
two very narrow peaks.  Our goal is to reproduce the original posterior, so we
adjust the temperature to $T=10,000$.  Taking logs, we get the target as shown
in the far left of Figure~\ref{fig:gauss_mix_1}.

We ran MCMC with with our test against the test
from~\citet{icml2014c1_bardenet14} and a simplified version
of~\citet{cutting_mh_2014}. Both methods use repeated testing which
must be discounted to bound overall test
accuracy. ~\citet{icml2014c1_bardenet14} conservatively partitions the
test error, while~\citet{cutting_mh_2014} used a complex dynamic
programming heuristic to estimate the overall test error. We did not
implement this heuristic and instead set the individual test error
equal to the overall test error. Thus our results for
~\citet{cutting_mh_2014} should be treated as lower bounds. All
methods were initialized with minibatch size 100.  For ~\citet{cutting_mh_2014} we
increment sizes by 100 and set the tolerance $\epsilon=0.005$.  For
~\citet{icml2014c1_bardenet14}, we increase sizes geometrically with $\gamma = 1.5$ and
use parameters $p = 2, \delta = 0.01$.  All methods collect 5000
samples using a random walk proposer with covariance ${\rm diag}(0.15,
0.15)$, which means the M-H test is responsible for shaping the sample
distribution.

@@

We discretize the posterior coordinates into bins with respect to the two
components of $\theta$.  The probability $P_i$ of a sample falling into bin $i$
is the integral of the true posterior over the bin's area.  A single sample
should therefore be multinomial with distribution $P$, and a set of $n$ (ideally
independent) samples is ${\rm Multinomial}(P,n)$. This distribution is simple
and we can use it to measure the quality of the samples rather than use general
purpose tests like KL-divergence or likelihood-ratio, which are problematic
with zero counts.

For large $n$, the per-bin distributions are approximated by Poissons with
parameter $\lambda_i=P_i n$. Given samples $\{\theta_1,\ldots,\theta_T\}$, let
$c_j$ denote the number of individual samples $\theta_i$ that fall in bin $j$
out of $N_{\rm bins}$ total. We have
\begin{equation}\label{eq:log_prob_poissons}
\begin{split}
    \log p(c_1, \ldots, c_{N_{\rm bins}} \mid P_1, \ldots, P_{N_{\rm bins}}) & =  \\
    \sum_{j=1}^{N_{\rm bins}} c_j \log (n P_j) - n P_j - \log(\Gamma(c_j+1)). & \\
\end{split}
\end{equation}
Table~\ref{tab:poissons} shows the likelihoods. To facilitate
interpretation we perform significance tests using Chi-Squared
distribution (also in Table~\ref{tab:poissons}). Scores lie
between~\citet{cutting_mh_2014} and~\citet{icml2014c1_bardenet14}, but
the variance of these values is high and ordering changes depending on
the range of samples generated.

Figure~\ref{fig:gauss_mix_2} shows that the new method dominates in
terms of speed and efficiency. The histograms of the (final) minibatch sizes
used each iteration show that our method consumes significantly less data; the
distribution is short-tailed and the mean is 210, more than an order of
magnitude better compared to the other two methods (averages are 15562 and
16857). The sizes correspond to the running times of the methods, since
they all consume linear time in data consumed.

@@

We next test logistic regression for the binary classification of 1s
versus 7s on a subset of the MNIST8M dataset, a larger version of
MNIST~\citep{lecun-mnisthandwrittendigit-2010}. We randomly subsampled
450k training and 192k testing points.
%%% The pixels are scaled in $[0,1]$  - JFC Why ????
We impose a uniform prior on $\theta$ and again use a random walk
proposer, this time with covariance matrix $0.05I$. The temperature is
set at $T=1000$. We run the three tests for samples and again use 100
as the starting minibatch size. Method~\citet{cutting_mh_2014} used
per-test error of $\epsilon=0.05$.  For~\citet{icml2014c1_bardenet14},
we used $\gamma=2.0$ (discounting factor). We tried to use the
symbolic bound for $C_{\theta,\theta'}$ for Logistic regression from
~\citet{icml2014c1_bardenet14}, but found it to be too high. Instead
we used the empirical $C_{\theta,\theta'}$ from the entire dataset
without including the test for this test, so again our results
represent a lower bound for this method.

@@

We show that the CLT error bound can be improved to $O(n^{-1})$ 
using a more precise limit distribution under an additional assumption. Let
$\mu_i$ denote the $i^{th}$ moment, and $b_i$ denote the $i^{th}$ absolute
moment of $X$. If Cramer's condition holds:
\begin{equation}\label{eq:cramers_condition}
    \lim_{t \to \infty} \sup |E(\exp(i t X))| < 1,
\end{equation}
then Equation 2.2 in Bentkus et al.'s work on Edgeworth
expansions~\citep{Bentkus97} provides:

@@

We previously submitted an early, incomplete draft of this paper to NIPS 2016. The
current manuscript has been substantially improved since that submission. We have
made the following changes:

\begin{enumerate}
\item The (incomplete) analysis in the NIPS paper has been substantially replaced.
  The asymptotic CLT arguments in the earlier paper have been replaced with
  explicit quantitative bounds. There were several gaps in the earlier analysis:
  the effects of addition of random variables on CDF errors and the construction and
  error bounds of the correction distribution which are key parts of the present
  paper have been added.

\item Several recent relevant references have been added, and we have written
  clearer statements about the contribution of the present work.
  These include~\citep{TallData15} and the Barker test~\citep{Barker65}.

\item Some reviewers mentioned that our deconvolution approach to
  determine the correction distribution was not unique and thus
  ill-defined.  We added detail description on how the correction
  distribution is computed. While the distribution is not unique, we
  regularize the inversion to obtain a concrete distribution with very
  low error (close to single-point machine precision).

\item The earlier draft had an inconsistency in its statement about constant
  minibatch size. We clarify that this is true only in expected value.

\item Our experiments now include new comparisons with a baseline
  from~\citep{icml2014c1_bardenet14} (in addition to~\citep{cutting_mh_2014},
  which we had earlier). In addition, each algorithm now runs MCMC sampling on
  the \emph{same} distribution.  Previously, we ran our distribution at a
  higher temperature but kept the algorithm from~\citep{cutting_mh_2014}
  running on the distribution at temperature $T=1$. In this set of
  experiments, we tuned hyperparameters of the other algorithms to yield
  best results. In the Gaussian mixture model scenario
  (Section~\ref{ssec:gaussians}), we provide likelihoods and test
  statistics to measure the accuracy of the samples.

@@

We estimate the degree of overlap between the papers in mathematics (equations) at less than
10\%, in overall text at less than 30\%. The experiments are similar but were also redone at larger
scale in this draft.
